### 2010-10-16 docs/architecture/architecture.tex
%ng -> nghost()
add some info on diag and compilation options

To build the MAESTRO executable, simply type `{\tt make}' in the
problem directory.  The executable will have a name like
{\tt main.Linux.Intel.exe}, where the specific parts of 
the name depend on the compilers and OS used.  Each problem
will have one or more inputs files (for example, {\tt test2/inputs\_2d})
which override the default values for one or more runtime parameters.
The code is run simply as:
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d
\end{verbatim}
As the code runs, it will output both plotfiles and checkpoints.
By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
the number {\em nnnnn} is the timestep number when the file was
outputted.  Similarly, the checkpoints are named {\tt chk}{\em
  nnnnn}.  BoxLib plotfiles and checkpoints are actually directories,
with the data stored in subdirectories grouped by refinement level.
Details of the simulation (number of processors used, output date,
output directory, runtime parameter values, ...) are stored in
the {\tt job\_info} file in each plotfile directory.

@@

@@

\begin{verbatim}
    ng_sp = s(1)%ng
\end{verbatim}

>>>>

To build the MAESTRO executable, simply type `{\tt make}' in the
problem directory.  The executable will have a name like
{\tt main.Linux.Intel.exe}, where the specific parts of 
the name depend on the compilers and OS used.  MAESTRO can be built
with support for parallelism (using MPI or OpenMPI), or compiled
as a serial code.  The top portion
of the {\tt GNUmakefile} can be editted to choose the build options.
Setting {\tt MPI := t} will build the code to use MPI for parallelization.
Setting {\tt OMP := t} will use OpenMP.  If desired, these are used together,
with MPI distributing the grids across the processors and within a 
shared-memory node, OpenMP is used to allow many cores to operate
on the same grid.  A final build option determines whether to build
the code with support for debugging.  Setting {\tt NDEBUG := t} disables
debugging features.

Each problem will have one or more inputs files (for example, {\tt
  test2/inputs\_2d}) which override the default values for one or more
runtime parameters.  The code is run simply as:
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d
\end{verbatim}
As the code runs, it will output both plotfiles and checkpoints.
By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
the number {\em nnnnn} is the timestep number when the file was
outputted.  Similarly, the checkpoints are named {\tt chk}{\em
  nnnnn}.  BoxLib plotfiles and checkpoints are actually directories,
with the data stored in subdirectories grouped by refinement level.
Details of the simulation (number of processors used, output date,
output directory, runtime parameter values, ...) are stored in
the {\tt job\_info} file in each plotfile directory.

@@

\subsubsection{Diagnostic Files}

By default, MAESTRO outputs global diagnostics each timestep into a file
called {\tt maestro\_diag.out}.  This includes the maximum Mach number,
peak temperature, and peak nuclear energy generation rate.  Individual problems
can provide their own {\tt diag.f90} file to produce custom diagnostic
output.

@@

\begin{verbatim}
    ng_sp = nghost(s(1))
\end{verbatim}
